Data Exploration

### 2021-10-14 code/processing_code/Data_Exploration.Rmd
Fixed Processing Script - CC

#### Loading the data from the processing script. Note that because you are loading a library at the beginning, it may either take a while or take several tries.
```{r}
MIDO <- readRDS("../../data/processed_data/MIDO.rds")
NORO <- readRDS("../../data/processed_data/NORO.rds")
BICO <- readRDS("../../data/processed_data/BICO.rds")
```

>>>>

#### Loading the data from the processing script. Note that because you are loading a library at the beginning, it may either take a while or take several tries.
```{r}
MIDO <- here::here("data","processed_data","MIDO.RDS")
NORO <- here::here("data","processed_data","NORO.RDS")
BICO <- here::here("data","processed_data","BICO.RDS")

readRDS(MIDO)
readRDS(NORO)
readRDS(BICO)
```
